### 2024-07-10 getting-started.qmd
20240706 - try indentation
20240706 - fix indentation
20240707 - Cite Intro to NFL Analytics
20240710 - blog instructions

1. Set up a free account on [GitHub.com](https://github.com).
1. Download GitHub Desktop: <https://desktop.github.com>
:::

@@

Below, we provide examples for how to download various types of football data.

>>>>

1. Set up a free account on [GitHub.com](https://github.com).
1. Download GitHub Desktop: <https://desktop.github.com>
1. Make sure you are logged into your GitHub account on [GitHub.com](https://github.com).
1. Go to the following GitHub repository: <https://github.com/isaactpetersen/QuartoBlogFantasyFootball> and complete the following steps:
  1. Click "Use this Template" (in the top right of the screen) > "Create a new repository"
  1. Make sure the checkbox is selected for the following option: "Include all branches"
  1. Make sure your Owner account is selected
  1. Specify the repository name to whatever you want, such as `FantasyFootballBlog`
  1. Type a brief description, such as `Files for my fantasy football blog`
  1. Keep the repository public (this is necessary for generating your blog)
  1. Select "Create repository"
1. After creating the new repository, make sure you are on the page of of your new repository and complete the following steps:
  1. Click "Settings" (in the topof the screen)
  1. Click "Actions" (in the left sidebar) > "General"
  1. Make sure the following are selected:
    - "Read and write permissions" (under "Workflow permissions")
    - "Allow GitHub Actions to create and approve pull requests"
    - then click "Save"
  1. Click "Pages" (in the left sidebar)
  1. Make sure the following are selected:
    - "Deploy from a branch" (under "Source")
    - "gh-pages/(root)" (under "Branch")
    - then click "Save"
1. Clone the repository to your local computer by clicking "Code" > "Open with GitHub Desktop", select the folder where you want the repository to be saved on your local computer, and click "Clone"
:::

@@

Below, we provide examples for how to download various types of National Football League (NFL) data.
For additional resources, @Congelio2023 provides a helpful introductory text for working with NFL data in `R`.
